Treatment_Outcomes

### 2023-04-17 Treatment_Outcomes.Rmd
Got pre/post scores. Can't figure out long data.

```{r}
#1. First adjust the their values for length of stay above 40 to 40, because the measures don't go above 40 days.
Mothership_Pre_Post <- Mothership
  mutate(Mothership_Pre_Post, 
            Days_complete_W = ifelse(Days_complete_1 > 40, 40,Days_complete_1)
         )

  Mothership
#2. Then create df with CUDOS and CUXOS scores
  # Depression

@@

#3. Extract the valeues for each patient at their last day (length of stay)
    # mutate(Mothership_Pre_Post, 
    #         CUDOS_post = CUDOS_Score[
    #           cbind(seq_along(Mothership_Pre_Post$Days_complete_W),
    #                 Mothership_Pre_Post$Days_complete_W)],
    #         CUXOS_post = CUXOS_Score[
    #           cbind(seq_along(Mothership_Pre_Post$Days_complete_W),
    #                 Mothership_Pre_Post$Days_complete_W)]
    #      )
```

```{r}
CUDOS_post = CUDOS_Score[cbind(seq_along(Mothership$ Days_complete_W),Mothership$ Days_complete_W)]
CUXOS_post = CUXOS_Score[cbind(seq_along(Mothership$ Days_complete_W),Mothership$ Days_complete_W)]

#4. Extract the value for their first day 
CUDOS_pre<-Mothership$Day1_CUDOS
CUXOS_pre<-Mothership$Day1_CUXOS
AnxDep_PrePost <- data.frame(cbind(Mothership$ID1,CUDOS_pre,CUDOS_post,CUXOS_pre,CUXOS_post))
AnxDep_PrePost

#5. Create long dataframe

###### This is where I am. I'm trying to figure out how to create the long dataset
AnxDep_PrePost_Long <- gather(AnxDep_PrePost,ID1:CUXOS_post)
                              factor_key = "T")

Mothership_Long_RDQ <- gather(Mothership_RDQ,rm,RDQ,rdqPRE_coping:rdqPOST_sym,
                              factor_key = "T")
Mothership_Long_RDQ <- Mothership_Long_RDQ[order(Mothership_Long_RDQ$ID1),]

?gather()

>>>>

```{r}
#1. First adjust the their values for length of stay above 40 to 40, because the measures don't go above 40 days.
Mothership_Pre_Post <- Mothership %>%
  mutate(Mothership_Pre_Post, 
            Days_complete_W = ifelse(Days_complete_1 > 40, 40,Days_complete_1)
         )

Mothership_Pre_Post$Days_complete_W

#2. Then create df with CUDOS and CUXOS scores
  # Depression

@@

#3. Extract the valeues for each patient at their last day (length of stay)
# Mothership_Pre_Post <- mutate(Mothership_Pre_Post,
#             CUDOS_post = CUDOS_post,
#             CUXOS_post = CUXOS_post)
    ##### Why is it not includeing NAs.

CUDOS_post = CUDOS_Score[cbind(seq_along(Mothership$ Days_complete_W),Mothership$ Days_complete_W)]
CUXOS_post = CUXOS_Score[cbind(seq_along(Mothership$ Days_complete_W),Mothership$ Days_complete_W)]

#4. Extract the value for their first day 
CUDOS_pre<-Mothership$Day1_CUDOS
CUXOS_pre<-Mothership$Day1_CUXOS
AnxDep_PrePost_test <- data.frame(cbind(Mothership$ID1,CUDOS_pre,CUDOS_post,CUXOS_pre,CUXOS_post))
AnxDep_PrePost_test
colnames(AnxDep_PrePost)[1] = "ID1"

## This is where I am Figure out where to go from here *******************
#5. Create long dataframe

AnxDep_PrePost_Lon <- gather(AnxDep_PrePost,ID1:CUXOS_post,factor_key = "T")

AnxDep_PrePost_Long <- pivot_longer(AnxDep_PrePost,ID1:CUXOS_post)

AnxDep_PrePost_Long
?pivot_longer()

AnxDep_PrePost_Long <- AnxDep_PrePost_Long[order(AnxDep_PrePost_Long$ID1),]

Mothership_Long_RDQ <- gather(Mothership_RDQ,rm,RDQ,rdqPRE_coping:rdqPOST_sym,
                              factor_key = "T")
Mothership_Long_RDQ
